My title

### 2024-11-27 paper/paper.qmd
fixed sample size in model_data.R

@@

# TABLE 1: CLEANED DATASET
data %>% head(5)
```

>>>>

The estimand of this paper is the probability that a book is highly-rated (has an average rating of over 4 on a 0-5 scale), based on book characteristics. It is difficult to measure the exact number as there are millions of children's books that are published and not all of them will be accessed due to various issues. For examples, children's books from different countries may have different ratings. Therefore in this paper, we attempt to estimate the estimand using a logistic regression model which is fitted using a sample from the Children's Book Rating dataset (CITATION)

# Data

Data analysis is performed using statistical programming language , along with packages

@@

# TABLE 1: CLEANED DATASET
data %>% head(5)

data
```
